---
title: "Modelling the impact of inundative sterile parasitoids and SIT as a novel combination for insect pest eradication"
subtitle: "*Document structure and formatting were assisted with Cursor.*"
author: "Dr Tom Moore - Statistical Scientist"
date: "`r Sys.Date()`"
format:
  html:
    include-in-header:
      text: |
        <style>
        .quarto-title .subtitle,
        p.subtitle,
        .subtitle.lead {
          font-size: 0.88rem;
          font-weight: normal;
        }
        </style>
    code-fold: false
    toc: true
    toc-float: true
    toc-depth: 5
    theme: united
    highlight-style: tango
    fig-width: 9
    fig-height: 6
    df-print: paged
    fig-dpi: 600
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup-packages
#| include: false

# Project root is resolved with `here` (see .here at repo root). Minimal dependencies for
# this document: GLMMs (lme4, glmmTMB), effects plots (effects), diagnostics (performance), contrasts
# (emmeans), Excel reads (readxl), cleaning (janitor), ggplot/tidy data (tidyverse), HTML tables
# (kableExtra). Figures are written under outputs/plots via ggsave in the figure chunks below.

ipak <- function(pkg) {
  new.pkg <- pkg[!(pkg %in% installed.packages()[,"Package"])]
  if (length(new.pkg)) {
    install.packages(new.pkg, dependencies = TRUE)
    cat("Not Installed:", paste(new.pkg, collapse = ", "), "\n")
  } else {
    cat("All Packages Installed :) \n")
  }
  invisible(sapply(pkg, require, character.only = TRUE))
}

packages <- c(
  "tidyverse", "readxl", "janitor", "lme4", "glmmTMB", "effects",
  "performance", "emmeans", "here", "MuMIn", "kableExtra"
)
ipak(packages)
```

```{r}
#| label: setup-wd
#| include: false

# Uncomment for strict here() resolution from this file:
# here::i_am("scripts/1_analysis.qmd")

dir.create(here::here("outputs/plots"), recursive = TRUE, showWarnings = FALSE)

# Models tab (all figures): AICc (1 dp), response (family + link), df, formula; sorted by AICc
models_aicc_table_with_response <- function(...) {
  objs <- Filter(Negate(is.null), list(...))
  if (!length(objs)) {
    stop("No non-NULL models passed to models_aicc_table_with_response")
  }
  aicc <- vapply(objs, MuMIn::AICc, numeric(1))
  npar <- vapply(objs, function(m) attr(stats::logLik(m), "df"), numeric(1))
  frml <- vapply(objs, function(m) {
    paste(deparse(stats::formula(m), width.cutoff = 500), collapse = " ")
  }, character(1))
  resp <- vapply(objs, function(m) {
    fam <- tryCatch(stats::family(m), error = function(e) NULL)
    if (is.null(fam)) {
      return("—")
    }
    ff <- fam$family
    lk <- fam$link
    # glmer.nb: fam$family is like "Negative Binomial(9.416)" — θ is the fitted NB parameter, not part of the link
    if (is.character(ff) && grepl("^Negative Binomial\\(", ff)) {
      ff <- "negative binomial"
    }
    paste0(ff, " (", lk, ")")
  }, character(1))
  ord <- order(aicc)
  tab <- data.frame(
    AICc = round(aicc[ord], 1),
    response = resp[ord],
    df = as.integer(round(npar[ord])),
    `model formula` = frml[ord],
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  rownames(tab) <- NULL
  tab
}

# Styled HTML table: small font.
# highlight_row: single row index to highlight; if NULL and fallback_best_aicc, highlights row 1 (lowest AICc after sorting).
kable_models_aicc_html <- function(tab, highlight_row = NULL, fallback_best_aicc = TRUE) {
  kb <- knitr::kable(tab, format = "html", escape = FALSE)
  kb <- kableExtra::kable_styling(
    kb,
    full_width = FALSE,
    bootstrap_options = c("striped", "hover"),
    font_size = 8
  )
  hr <- NULL
  if (length(highlight_row) == 1L && !is.na(highlight_row) &&
      highlight_row >= 1L && highlight_row <= nrow(tab)) {
    hr <- as.integer(highlight_row)
  } else if (isTRUE(fallback_best_aicc) && nrow(tab) >= 1L) {
    hr <- 1L
  }
  if (!is.null(hr)) {
    kb <- kableExtra::row_spec(kb, hr, bold = TRUE, background = "#fff3cd")
  }
  kb
}

# Figure 5 table: binomial `cbind(...) ~ cage_id + (1|replicate) + (1|obs)` without egg-mass terms (m3)
fig5_highlight_row_olre_binomial <- function(tab) {
  f <- tab$`model formula`
  has_rep <- grepl("(1 | replicate)", f, fixed = TRUE) | grepl("(1|replicate)", f, fixed = TRUE)
  has_obs <- grepl("(1 | obs)", f, fixed = TRUE) | grepl("(1|obs)", f, fixed = TRUE)
  w <- which(
    has_rep & has_obs &
      !grepl("total_egg_mass", f, fixed = TRUE) &
      grepl("cbind", f, fixed = TRUE) &
      grepl("^binomial \\(", tab$response, ignore.case = TRUE)
  )
  if (length(w) == 1L) w else integer(0)
}

# Figure 6 table: `no_eggs ~ cage_id + (1 | replicate)` negative binomial, no OLRE, no offset (m1)
fig6_highlight_row_nb_replicate_only <- function(tab) {
  f <- tab$`model formula`
  has_rep <- grepl("(1 | replicate)", f, fixed = TRUE) | grepl("(1|replicate)", f, fixed = TRUE)
  has_obs <- grepl("(1 | obs)", f, fixed = TRUE) | grepl("(1|obs)", f, fixed = TRUE)
  w <- which(
    has_rep &
      !has_obs &
      grepl("^negative binomial", tab$response, ignore.case = TRUE) &
      !grepl("offset\\(", f)
  )
  if (length(w) == 1L) w else integer(0)
}

# Select fitted model with lowest AICc (for effects, validation, contrasts, summary)
pick_best_by_aicc <- function(...) {
  objs <- Filter(Negate(is.null), list(...))
  if (!length(objs)) {
    stop("No non-NULL models passed to pick_best_by_aicc")
  }
  aicc <- vapply(objs, MuMIn::AICc, numeric(1))
  objs[[which.min(aicc)]]
}

# Text line(s) printed above validation plots
format_model_formula <- function(m) {
  paste(deparse(stats::formula(m), width.cutoff = 500), collapse = " ")
}

# Fallback when performance::check_model() errors (e.g. binomial cbind / glmmTMB row alignment)
residual_fitted_diagnostic_plot <- function(m) {
  rf <- tryCatch(
    {
      r <- stats::residuals(m, type = "pearson")
      f <- stats::fitted(m)
      if (length(r) != length(f)) {
        NULL
      } else {
        data.frame(fitted = as.numeric(f), pearson_resid = as.numeric(r))
      }
    },
    error = function(e) NULL
  )
  if (is.null(rf) || nrow(rf) == 0L) {
    cat("*Could not build Pearson residual vs fitted fallback plot.*\n\n")
    return(invisible(NULL))
  }
  print(
    ggplot2::ggplot(rf, ggplot2::aes(x = fitted, y = pearson_resid)) +
      ggplot2::geom_point(alpha = 0.45, na.rm = TRUE) +
      ggplot2::geom_hline(yintercept = 0, linetype = 2, linewidth = 0.3) +
      ggplot2::labs(
        x = "Fitted values",
        y = "Pearson residuals",
        title = "Fallback diagnostic (check_model unavailable)"
      ) +
      ggplot2::theme_classic()
  )
}

safe_print_check_model <- function(m) {
  tryCatch(
    print(performance::check_model(m)),
    error = function(e) {
      cat(
        "*`performance::check_model()` failed:* ",
        conditionMessage(e),
        "\n\n",
        sep = ""
      )
      residual_fitted_diagnostic_plot(m)
    }
  )
}

# performance::check_model() for every named candidate (NULL → short note; use results: asis in chunk).
# section_labels: optional named character vector (same names as ...); appended to heading after model id.
validate_all_candidate_models <- function(..., section_labels = NULL) {
  lst <- list(...)
  nm <- names(lst)
  if (is.null(nm)) nm <- rep("", length(lst))
  for (i in seq_along(lst)) {
    id <- if (nzchar(nm[i])) nm[i] else paste0("model_", i)
    sub <- if (!is.null(section_labels) && id %in% names(section_labels)) {
      section_labels[[id]]
    } else {
      NULL
    }
    heading <- if (!is.null(sub)) paste0(id, " — ", sub) else id
    knitr::asis_output(paste0("\n\n#### ", heading, "\n\n"))
    m <- lst[[i]]
    if (is.null(m)) {
      cat("*This candidate did not fit (NULL).*\n\n")
      next
    }
    cat("Model formula:\n\n")
    cat(format_model_formula(m), "\n\n")
    safe_print_check_model(m)
  }
  invisible(NULL)
}

# Default plot labels for four cage levels (must match factor level order in the model)
pairwise_cage_display_four <- c("KWT", "SIT", "CBC", "Control")

# Figure 5: marginal means for cage_id (effects::allEffects for lme4/glm; emmeans for glmmTMB)
fig5_cage_effect_df <- function(m) {
  if (inherits(m, "glmmTMB")) {
    e <- emmeans::emmeans(m, ~ cage_id, type = "response")
    d <- as.data.frame(e)
    d$fit <- d$prob
    d$lower <- d$asymp.LCL
    d$upper <- d$asymp.UCL
    d
  } else {
    as.data.frame(effects::allEffects(m)[["cage_id"]])
  }
}

# Modeled values matching the effect plot + cage differences on response scale (under Effect plot tab)
kable_fig_modeled_estimates <- function(eff, cage_col, sex_col = NULL, scale_pct = FALSE) {
  cv <- eff[[cage_col]]
  if (!is.factor(cv)) cv <- factor(cv)
  disp <- pairwise_cage_display_four[as.integer(cv)]
  tab <- data.frame(
    `Cage treatment` = disp,
    check.names = FALSE,
    stringsAsFactors = FALSE
  )
  if (!is.null(sex_col) && sex_col %in% names(eff)) {
    tab$Sex <- stringr::str_to_title(as.character(eff[[sex_col]]))
  }
  mul <- if (scale_pct) 100 else 1
  tab$Estimate <- round(eff$fit * mul, 2)
  tab$Lower <- round(eff$lower * mul, 2)
  tab$Upper <- round(eff$upper * mul, 2)
  if (scale_pct) {
    names(tab)[names(tab) == "Estimate"] <- "Estimate (%)"
    names(tab)[names(tab) == "Lower"] <- "Lower (%)"
    names(tab)[names(tab) == "Upper"] <- "Upper (%)"
  }
  kb <- knitr::kable(
    tab,
    format = "html",
    digits = 2,
    caption = "Modeled estimates (same scale as the figure, with 95% confidence intervals).",
    escape = FALSE,
    table.attr = "style=\"margin-left:0;margin-right:auto;\""
  )
  kableExtra::kable_styling(
    kb,
    full_width = FALSE,
    bootstrap_options = c("striped", "hover"),
    font_size = 10,
    position = "left"
  )
}

kable_cage_pairwise_response <- function(m, cage_var, caption_suffix = NULL, diff_as_pct = FALSE) {
  form <- stats::as.formula(paste0("~ ", cage_var))
  emm <- emmeans::emmeans(m, form, type = "response")
  pr <- pairs(emmeans::regrid(emm, transform = "response"), reverse = TRUE)
  d <- as.data.frame(summary(pr))
  mf <- tryCatch(stats::model.frame(m), error = function(e) NULL)
  if (!is.null(mf) && cage_var %in% names(mf)) {
    x <- mf[[cage_var]]
    if (!is.factor(x)) x <- factor(x)
    levs <- levels(droplevels(x))
    n <- length(levs)
    disp <- if (n == length(pairwise_cage_display_four)) {
      pairwise_cage_display_four
    } else {
      levs
    }
    names(disp) <- levs
    d$contrast <- vapply(
      strsplit(as.character(d$contrast), " - ", fixed = TRUE),
      function(parts) {
        mapped <- unname(disp[parts])
        mapped[is.na(mapped)] <- parts[is.na(mapped)]
        paste(mapped, collapse = " - ")
      },
      FUN.VALUE = character(1),
      USE.NAMES = FALSE
    )
  }
  if (isTRUE(diff_as_pct)) {
    d$estimate <- d$estimate * 100
    d$SE <- d$SE * 100
  }
  d$estimate <- round(d$estimate, 2)
  d$SE <- round(d$SE, 2)
  d$p.value <- round(d$p.value, 2)
  cap <- if (isTRUE(diff_as_pct)) {
    paste0(
      "Pairwise differences between cage treatments (percentage points on modelled mortality ",
      "probability; Tukey-adjusted p-values)."
    )
  } else {
    "Pairwise differences between cage treatments (response scale; Tukey-adjusted p-values)."
  }
  if (!is.null(caption_suffix)) {
    cap <- paste(cap, caption_suffix)
  }
  cn <- if (isTRUE(diff_as_pct)) {
    c("Contrast", "Estimate (%)", "SE (%)", "p")
  } else {
    c("Contrast", "Estimate", "SE", "p")
  }
  kb <- knitr::kable(
    d[c("contrast", "estimate", "SE", "p.value")],
    format = "html",
    digits = c(NA, 2, 2, 2),
    caption = cap,
    col.names = cn,
    escape = FALSE,
    table.attr = "style=\"margin-left:0;margin-right:auto;\""
  )
  kableExtra::kable_styling(
    kb,
    full_width = FALSE,
    bootstrap_options = c("striped", "hover"),
    font_size = 10,
    position = "left"
  )
}

# Figure 5: caterpillar-style random effects (lme4 plot method; ggplot for glmmTMB)
print_fig5_random_effects <- function(m) {
  if (inherits(m, "glmmTMB")) {
    re <- lme4::ranef(m, condVar = TRUE)
    if (!length(re$cond)) {
      cat("No conditional random effects in this glmmTMB fit.\n")
      return(invisible(NULL))
    }
    for (nm in names(re$cond)) {
      bl <- re$cond[[nm]]
      cv <- attr(bl, "condVar")
      if (nrow(bl) == 1L && ncol(bl) > 1L) {
        # e.g. AR(1): one row, one column per sequential batch level (wide matrix)
        est <- as.numeric(bl[1, , drop = TRUE])
        lvl <- colnames(bl)
        se <- if (!is.null(cv) && length(dim(cv)) == 3L && dim(cv)[1L] > 1L) {
          sqrt(diag(cv[, , 1L]))
        } else {
          rep(NA_real_, length(est))
        }
        rdf <- data.frame(level = lvl, estimate = est, se = se)
      } else {
        se <- if (!is.null(cv) && length(dim(cv)) == 3L) sqrt(cv[1, 1, ]) else rep(NA_real_, nrow(bl))
        rdf <- data.frame(level = rownames(bl), estimate = bl[[1]], se = se)
      }
      p <- ggplot2::ggplot(rdf, ggplot2::aes(x = reorder(level, estimate), y = estimate)) +
        ggplot2::geom_point() +
        ggplot2::geom_errorbar(
          ggplot2::aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se),
          width = 0.2
        ) +
        ggplot2::coord_flip() +
        ggplot2::labs(title = paste0("Random effects: ", nm), x = NULL, y = "BLUP (link scale)")
      print(p)
    }
  } else if (inherits(m, "merMod")) {
    print(plot(lme4::ranef(m, condVar = TRUE)))
  } else {
    cat("No random effects in the selected model (fixed-effects GLM).\n")
  }
}
```

This document is **supporting information** for the paper *Modelling the impact of inundative sterile parasitoids and SIT as a novel combination for insect pest eradication*.

# Methods

## Statistical Analyses
Frequentist analyses in R (R Core Team, 2022) used **`glm`** and **`lme4`** mixed models (`glmer`, `glmer.nb`). **Diagnostics** came before **AICc** (Burnham & Anderson, 2002): a model was not chosen on **AICc** alone if **performance** checks were poor. **AICc** for **Figures 5–8** is in each Models tab. Usually the lowest-AICc **adequate** fit drives plots and tables; **Figures 5–6** instead use **fixed** reporting models (below).

**Checks:** `performance::check_model()` (Lüdecke et al., 2021), or residual–vs–fitted fallback. Validation runs on the fixed fits for **5–6** and on **every** candidate for **7–8**.

**Presentation:** Factor A–D → **KWT, SIT, CBC, Control**. Effect means: **`effects`** (Fox & Weisberg, 2019). Cage **pairwise** contrasts on the **response** scale: **`emmeans`**, Tukey adjustment (Lenth, 2024). **`ggplot2`** (Wickham, 2016).

- **Figure 5** — Binomial F1 mortality; replicate, **`(1|obs)`** (overdispersion), optional egg mass. **Fixed report model:** **`cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate) + (1|obs)`** (m3).
- **Figure 6** — Negative binomial egg counts; OLRE/offset variants compared. **Fixed report model:** **`no_eggs ~ cage_id + (1|replicate)`** (m1).
- **Figures 7–8** — Poisson adult mortality: cage, `+ sex`, `× sex`; lowest AICc for outputs.
- **Figures 9–10** — Descriptive plots only.

# Figure 5

**Wrangling & Summary**

```{r}
#| label: fig5-wrangling

# Read and prepare data for Figure 5
df_f5 <- read_excel(here::here("analysis/data/Cages datasheet actual.xlsx"),
                    sheet = "F1 egg mortality data") |>
  janitor::clean_names() |>
  mutate(replicate = replicate_2)|>
  group_by(cage_id, replicate) |>
  mutate(total_egg_mass = max(egg_mass)) |>
  ungroup() |>
  mutate(cage_id = as.factor(cage_id),
         replicate = as.factor(replicate),
         no_eggs = ifelse(f1_not_emerged == 0, 0, no_eggs),
         ) |>
  select(cage_id, replicate, total_egg_mass, f1_not_emerged, no_eggs) |>
  mutate(obs = factor(row_number()))

# Check data structure (tibble summary: rows × cols, classes, column types)
str(as_tibble(df_f5), vec.len = 2)
```

```{r}
#| label: fig5-models-run
#| include: false

# Fit models for Figure 5 (runs before Effect plot tab; shown again under Models tab)
fit_f5 <- function(expr, id) {
  tryCatch(expr, error = function(e) {
    warning("Figure 5 model ", id, " failed to fit: ", conditionMessage(e))
    NULL
  })
}

m1 <- glm(cbind(f1_not_emerged, no_eggs) ~ cage_id, family = binomial(link = "logit"), data = df_f5)
m2 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate), family = binomial(link = "logit"), data = df_f5)
# m3–m5: replicate + OLRE; variants with total egg mass (same random structure)
m3 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate) + (1|obs), family = binomial(link = "logit"), data = df_f5)
m4 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + total_egg_mass + (1|replicate) + (1|obs), family = binomial(link = "logit"), data = df_f5)
m5 <- fit_f5(
  glmer(
    cbind(f1_not_emerged, no_eggs) ~ cage_id * total_egg_mass + (1|replicate) + (1|obs),
    family = binomial(link = "logit"),
    data = df_f5
  ),
  "m5"
)

m_best <- pick_best_by_aicc(m1, m2, m3, m4, m5)
# Reporting model: binomial GLMM m3 — `cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate) + (1|obs)`
m_fig5 <- if (!is.null(m3)) m3 else if (!is.null(m2)) {
  warning("Figure 5: m3 (binomial OLRE) is NULL; using m2 for reporting.")
  m2
} else {
  warning("Figure 5: using m1 for reporting.")
  m1
}
```

::: {.panel-tabset}
## Effect plot
```{r}
#| label: fig5-effects
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Generate and plot effects for Figure 5 (m_fig5: binomial m3, replicate + OLRE)
eff <- fig5_cage_effect_df(m_fig5)

# Create plot
p_fig5 <- ggplot() +
  theme_classic() +
  geom_jitter(data = df_f5 %>%
  mutate(prop = ifelse(is.nan(f1_not_emerged/no_eggs), 0, f1_not_emerged/no_eggs)),
               aes(x = cage_id, y = prop),
              alpha = 0.14, width = 0.2, color = "grey30") +
  geom_point(data = eff,
              aes(x = cage_id, y = fit), size = 2) +
  geom_errorbar(data = eff,
    aes(x = cage_id, ymin = lower, ymax = upper), size = 1, width = 0.3) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("KWT", "SIT", "CBC", "Control")) +
  labs(x = "Cage treatment", y = "Percentage F1 egg mortality")

ggsave(
  filename = here::here("outputs/plots", "fig5.png"),
  plot = p_fig5,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_fig5
```

### Modeled estimates and pairwise differences

```{r}
#| label: fig5-contrasts
#| results: asis

# Figure 5: modeled estimates (figure scale) and pairwise cage differences (response scale)
knitr::asis_output('<div style="text-align:left;">\n')
print(kable_fig_modeled_estimates(fig5_cage_effect_df(m_fig5), "cage_id", scale_pct = TRUE))
print(kable_cage_pairwise_response(m_fig5, "cage_id", diff_as_pct = TRUE))
knitr::asis_output('</div>\n')
```

## Models
```{r}
#| label: fig5-models
#| eval: false

# Fit models for Figure 5
m1 <- glm(cbind(f1_not_emerged, no_eggs) ~ cage_id, family = binomial(link = "logit"), data = df_f5)
m2 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate), family = binomial(link = "logit"), data = df_f5)
m3 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate) + (1|obs), family = binomial(link = "logit"), data = df_f5)
m4 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id + total_egg_mass + (1|replicate) + (1|obs), family = binomial(link = "logit"), data = df_f5)
m5 <- glmer(cbind(f1_not_emerged, no_eggs) ~ cage_id * total_egg_mass + (1|replicate) + (1|obs), family = binomial(link = "logit"), data = df_f5)
m_best <- pick_best_by_aicc(m1, m2, m3, m4, m5)
m_fig5 <- if (!is.null(m3)) m3 else if (!is.null(m2)) m2 else m1

# Model selection
tab_f5 <- models_aicc_table_with_response(m1, m2, m3, m4, m5)
hr_f5_tab <- fig5_highlight_row_olre_binomial(tab_f5)
print(kable_models_aicc_html(
  tab_f5,
  highlight_row = if (length(hr_f5_tab) == 1L) hr_f5_tab else NULL,
  fallback_best_aicc = FALSE
))
```

```{r}
#| label: fig5-models-output
#| results: asis

tab_f5 <- models_aicc_table_with_response(m1, m2, m3, m4, m5)
hr_f5_tab <- fig5_highlight_row_olre_binomial(tab_f5)
print(kable_models_aicc_html(
  tab_f5,
  highlight_row = if (length(hr_f5_tab) == 1L) hr_f5_tab else NULL,
  fallback_best_aicc = FALSE
))
```

## Validation
```{r}
#| label: fig5-validation
#| fig-width: 10
#| fig-height: 10
#| results: asis

# Reporting model m3: binomial (logit) `cbind(f1_not_emerged, no_eggs) ~ cage_id + (1|replicate) + (1|obs)`
validate_all_candidate_models(
  m3 = m3,
  section_labels = c(m3 = "conditional **binomial** (logit link); `lme4::glmer`")
)
```

## Output
```{r}
#| label: fig5-output

# Model summary for Figure 5 (m_fig5: binomial m3, replicate + OLRE)
summary(m_fig5)
```

## Random effects
```{r}
#| label: fig5-random

# Random effects for m_fig5 (replicate + observation-level, binomial glmer)
print_fig5_random_effects(m_fig5)
```
:::

# Figure 6

**Wrangling & Summary**

```{r}
#| label: fig6-wrangling

# Read and prepare data for Figure 6
df_f6 <- read_excel(here::here("analysis/data/Cages datasheet actual.xlsx"),
                    sheet = "F1 egg mortality data") |>
  janitor::clean_names() |>
  mutate(replicate = replicate_2)|>
  select(cage_id, replicate, no_eggs) |>
  mutate(cage_id = as.factor(cage_id),
         replicate = as.factor(replicate),
         obs = factor(row_number()))

# Check data structure
str(df_f6)
```

```{r}
#| label: fig6-models-run
#| include: false

# Fit models for Figure 6 (runs before Effect plot tab; shown again under Models tab)
fit_f6 <- function(expr, id) {
  tryCatch(expr, error = function(e) {
    warning("Figure 6 model ", id, " failed to fit: ", conditionMessage(e))
    NULL
  })
}

# m1–m2: negative binomial; m3–m4: same + offset(log(pmax(no_eggs, 1))) (not stored in tibble)
m1 <- glmer.nb(no_eggs ~ cage_id + (1|replicate), data = df_f6)
m2 <- fit_f6(
  glmer.nb(no_eggs ~ cage_id + (1|replicate) + (1|obs), data = df_f6),
  "m2"
)
m3 <- fit_f6(
  glmer.nb(
    no_eggs ~ cage_id + (1|replicate) + offset(log(pmax(as.numeric(no_eggs), 1))),
    data = df_f6
  ),
  "m3"
)
m4 <- fit_f6(
  glmer.nb(
    no_eggs ~ cage_id + (1|replicate) + (1|obs) + offset(log(pmax(as.numeric(no_eggs), 1))),
    data = df_f6
  ),
  "m4"
)

m_best <- pick_best_by_aicc(m1, m2, m3, m4)
# Reporting model: NB GLMM m1 — no_eggs ~ cage_id + (1|replicate)
m_fig6 <- m1
```

::: {.panel-tabset}
## Effect plot
```{r}
#| label: fig6-effects
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Generate and plot effects for Figure 6 (m_fig6 = m1: replicate random intercept only)
eff <- as.data.frame(
  effects::allEffects(m_fig6,
                      )[["cage_id"]])

# Create plot
p_fig6 <- ggplot() +
  theme_classic() +
  geom_jitter(data = df_f6,
              aes(x = cage_id, y = no_eggs),
              alpha = 0.14, width = 0.2, color = "grey30") +
  geom_point(data = eff,
             aes(x = cage_id, y = fit), size = 2) +
  geom_errorbar(data = eff,
    aes(x = cage_id, ymin = lower, ymax = upper), size = 1, width = 0.3) +
  scale_y_continuous(limits = c(0,100)) +
  scale_x_discrete(labels = c("KWT", "SIT", "CBC", "Control")) +
  labs(x = "Cage treatment", y = "Eggs per mass")

ggsave(
  filename = here::here("outputs/plots", "fig6.png"),
  plot = p_fig6,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_fig6
```

### Modeled estimates and pairwise differences

```{r}
#| label: fig6-contrasts
#| results: asis

# Figure 6: modeled estimates (figure scale) and pairwise cage differences (response scale)
knitr::asis_output('<div style="text-align:left;">\n')
eff_f6_tab <- as.data.frame(effects::allEffects(m_fig6)[["cage_id"]])
print(kable_fig_modeled_estimates(eff_f6_tab, "cage_id", scale_pct = FALSE))
print(kable_cage_pairwise_response(m_fig6, "cage_id"))
knitr::asis_output('</div>\n')
```

## Models
```{r}
#| label: fig6-models
#| eval: false

# Fit models for Figure 6
m1 <- glmer.nb(no_eggs ~ cage_id + (1|replicate), data = df_f6)
m2 <- glmer.nb(no_eggs ~ cage_id + (1|replicate) + (1|obs), data = df_f6)
m3 <- glmer.nb(
  no_eggs ~ cage_id + (1|replicate) + offset(log(pmax(as.numeric(no_eggs), 1))),
  data = df_f6
)
m4 <- glmer.nb(
  no_eggs ~ cage_id + (1|replicate) + (1|obs) + offset(log(pmax(as.numeric(no_eggs), 1))),
  data = df_f6
)
m_best <- pick_best_by_aicc(m1, m2, m3, m4)
m_fig6 <- m1

# Model selection
tab_f6 <- models_aicc_table_with_response(m1, m2, m3, m4)
hr_f6_tab <- fig6_highlight_row_nb_replicate_only(tab_f6)
print(kable_models_aicc_html(
  tab_f6,
  highlight_row = if (length(hr_f6_tab) == 1L) hr_f6_tab else NULL,
  fallback_best_aicc = FALSE
))
```

```{r}
#| label: fig6-models-output
#| results: asis

tab_f6 <- models_aicc_table_with_response(m1, m2, m3, m4)
hr_f6_tab <- fig6_highlight_row_nb_replicate_only(tab_f6)
print(kable_models_aicc_html(
  tab_f6,
  highlight_row = if (length(hr_f6_tab) == 1L) hr_f6_tab else NULL,
  fallback_best_aicc = FALSE
))
```

## Validation
```{r}
#| label: fig6-validation
#| fig-width: 10
#| fig-height: 10
#| results: asis

# Validation for reporting model m1 only: no_eggs ~ cage_id + (1|replicate), negative binomial
validate_all_candidate_models(
  m1 = m1,
  section_labels = c(
    m1 = "**negative binomial** (log link); `lme4::glmer.nb`; `no_eggs ~ cage_id + (1|replicate)`"
  )
)
```

## Output
```{r}
#| label: fig6-output

# Model summary for Figure 6 (m_fig6 = m1)
summary(m_fig6)
```

## Random effects
```{r}
#| label: fig6-random

# Random effects for m_fig6 (replicate only)
print(plot(ranef(m_fig6, condVar = TRUE)))
```
:::

# Figures 7 & 8

**Wrangling & Summary**

```{r}
#| label: fig7-8-wrangling

# Read and prepare data for Figures 7 & 8
df_f7_8 <- read_excel(here::here("analysis/data/Cages datasheet actual.xlsx"),
                    sheet = "Adult mortality data") |>
  janitor::clean_names() |>
  select(cage_id2, no_died_male, no_died_female) |>
  pivot_longer(
    cols = c(no_died_male, no_died_female),
    names_to = "sex",
    values_to = "mortality"
  ) |>
  mutate(sex = case_when(
    sex == "no_died_male" ~ "male",
    sex == "no_died_female" ~ "female",
    TRUE ~ NA_character_
  )) |>
  filter(!(is.na(mortality)))

# Check data structure
str(df_f7_8)
```

```{r}
#| label: fig7-8-models-run
#| include: false

# Fit models for Figures 7 & 8 (runs before Effect plot tab; shown again under Models tab)
# m1: cage only; m2: add sex; m3: cage × sex
m1 <- glm(mortality ~ cage_id2, family = poisson(), data = df_f7_8)
m2 <- glm(mortality ~ cage_id2 + sex, family = poisson(), data = df_f7_8)
m3 <- glm(mortality ~ cage_id2 * sex, family = poisson(), data = df_f7_8)
m_best <- pick_best_by_aicc(m1, m2, m3)
```

::: {.panel-tabset}
## Effect plot
```{r}
#| label: fig7-8-effects
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Generate and plot effects for Figures 7 & 8 (lowest AICc model)
fig78_has_sex <- any(grepl("sex", attr(stats::terms(stats::formula(m_best)), "term.labels")))

if (fig78_has_sex) {
  eff <- as.data.frame(effects::Effect(c("cage_id2", "sex"), m_best))
  p_fig78 <- ggplot() +
    theme_classic() +
    geom_point(
      data = df_f7_8,
      aes(x = cage_id2, y = mortality, color = sex),
      alpha = 0.28,
      position = position_jitter(width = 0.2, height = 0)
    ) +
    geom_point(
      data = eff,
      aes(x = cage_id2, y = fit, color = sex),
      shape = 16,
      size = 2,
      position = position_dodge(0.5)
    ) +
    geom_errorbar(
      data = eff,
      aes(x = cage_id2, ymin = lower, ymax = upper, color = sex),
      linewidth = 0.8,
      width = 0.3,
      position = position_dodge(width = 0.5)
    ) +
    scale_y_continuous(limits = c(0, 5)) +
    scale_x_discrete(labels = c("KWT", "SIT", "CBC", "Control")) +
    scale_color_brewer(palette = "Set1", labels = c("Female", "Male")) +
    labs(
      x = "Cage treatment",
      y = expression("Number of dead "*italic(Nezara~viridula)),
      color = "Sex"
    ) +
    theme(legend.position = "right")
} else {
  eff <- as.data.frame(effects::Effect("cage_id2", m_best))
  p_fig78 <- ggplot() +
    theme_classic() +
    geom_point(
      data = df_f7_8,
      aes(x = cage_id2, y = mortality, color = sex),
      alpha = 0.28,
      position = position_jitter(width = 0.2, height = 0)
    ) +
    geom_point(data = eff, aes(x = cage_id2, y = fit), inherit.aes = FALSE, size = 2, shape = 16) +
    geom_errorbar(
      data = eff,
      aes(x = cage_id2, ymin = lower, ymax = upper),
      inherit.aes = FALSE,
      linewidth = 0.8,
      width = 0.25
    ) +
    scale_y_continuous(limits = c(0, 5)) +
    scale_x_discrete(labels = c("KWT", "SIT", "CBC", "Control")) +
    scale_color_brewer(palette = "Set1", labels = c("Female", "Male")) +
    labs(
      x = "Cage treatment",
      y = expression("Number of dead "*italic(Nezara~viridula)),
      color = "Sex",
      subtitle = "Fitted means: cage effect only (no sex in selected model)"
    ) +
    theme(legend.position = "right")
}

ggsave(
  filename = here::here("outputs/plots", "fig7-8.png"),
  plot = p_fig78,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_fig78
```

### Modeled estimates and pairwise differences

```{r}
#| label: fig7-8-contrasts
#| results: asis

# Figures 7 & 8: modeled estimates (figure scale) and pairwise cage differences (response scale)
fig78_has_sex <- any(grepl("sex", attr(stats::terms(stats::formula(m_best)), "term.labels")))
knitr::asis_output('<div style="text-align:left;">\n')
if (fig78_has_sex) {
  eff_f78_tab <- as.data.frame(effects::Effect(c("cage_id2", "sex"), m_best))
  print(kable_fig_modeled_estimates(eff_f78_tab, "cage_id2", sex_col = "sex", scale_pct = FALSE))
  print(kable_cage_pairwise_response(
    m_best,
    "cage_id2",
    "Marginal means are averaged equally over sex when comparing cages."
  ))
} else {
  eff_f78_tab <- as.data.frame(effects::Effect("cage_id2", m_best))
  print(kable_fig_modeled_estimates(eff_f78_tab, "cage_id2", scale_pct = FALSE))
  print(kable_cage_pairwise_response(m_best, "cage_id2"))
}
knitr::asis_output('</div>\n')
```

## Models
```{r}
#| label: fig7-8-models
#| eval: false

# Fit models for Figures 7 & 8
m1 <- glm(mortality ~ cage_id2, family = poisson(), data = df_f7_8)
m2 <- glm(mortality ~ cage_id2 + sex, family = poisson(), data = df_f7_8)
m3 <- glm(mortality ~ cage_id2 * sex, family = poisson(), data = df_f7_8)
m_best <- pick_best_by_aicc(m1, m2, m3)

# Model selection
tab_f78 <- models_aicc_table_with_response(m1, m2, m3)
print(kable_models_aicc_html(tab_f78))
```

```{r}
#| label: fig7-8-models-output
#| results: asis

tab_f78 <- models_aicc_table_with_response(m1, m2, m3)
print(kable_models_aicc_html(tab_f78))
```

## Validation
```{r}
#| label: fig7-8-validation
#| fig-width: 10
#| fig-height: 10
#| results: asis

# Model validation for Figures 7 & 8 (all candidate models)
validate_all_candidate_models(m1 = m1, m2 = m2, m3 = m3)
```

## Output
```{r}
#| label: fig7-8-output

# Model summary for Figures 7 & 8 (lowest AICc model)
summary(m_best)
```
:::

# Figure 9

**Wrangling & Summary**

```{r}
#| label: fig9-wrangling

# Read and prepare data for Figure 9
df_f9a <- read_excel(here::here("analysis/data/Lincoln SIT alone.xlsx"),
                    sheet = "Sheet1") |>
  janitor::clean_names() |>
  select(cross, percent_mortality) |>
  mutate(cross = as.factor(cross)) |>
  mutate(data = "Experiment") |>
  filter(!(is.na(cross)))

df_f9b <- read_excel(here::here("analysis/data/Model SIT alone.xlsx"),
                    sheet = "Sheet1") |>
  janitor::clean_names() |>
  select(cross, percent_mortality) |>
  mutate(cross = as.factor(cross)) |>
  mutate(data = "Model") |>
  filter(!(is.na(percent_mortality)))

# Combine experimental and model data
df_f9 <- rbind(df_f9a, df_f9b)
rm(df_f9a, df_f9b)

# Check data structure
str(df_f9)
```

::: {.panel-tabset}
## Plot 1
```{r}
#| label: fig9-plota
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 9
p_f9a <- ggplot(df_f9,
       aes(x = cross, y = 1-percent_mortality, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  #scale_y_log10(labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("0:1", "1:1", "4:1", "8:1")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent F1 egg fertility", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig9a.png"),
  plot = p_f9a,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f9a
```

## Models

No statistical model is fitted in this figure; panels compare experimental and model outputs descriptively.

## Plot 2
```{r}
#| label: fig9-plotb
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 9
p_f9b <- ggplot(df_f9,
       aes(x = cross, y = percent_mortality, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  geom_boxplot(
    aes(x = cross, y = percent_mortality),
    alpha = 0.2,
    position = position_dodge(width = 0.5)
  ) +
  
  #scale_y_log10(labels = scales::percent_format(accuracy = 1)) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("0:1", "1:1", "4:1", "8:1")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent F1 egg mortality", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig9b.png"),
  plot = p_f9b,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f9b
```
## Plot 3
```{r}
#| label: fig9-plotc
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 9
p_f9c <- ggplot(df_f9,
       aes(x = cross, y = percent_mortality, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  geom_boxplot(
    aes(x = cross, y = percent_mortality),
    alpha = 0.2,
    position = position_dodge(width = 0.5)
  ) +
  # Add mean values as asterisks
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 8,  # asterisk shape
    size = 3,
    color = "red",
    position = position_dodge(width = 0.5),
    show.legend = FALSE
  ) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("0:1", "1:1", "4:1", "8:1")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent F1 egg mortality", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig9c.png"),
  plot = p_f9c,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f9c
```
## Plot 4
```{r}
#| label: fig9-plotd
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 9
p_f9d <- ggplot(df_f9,
       aes(x = cross, y = percent_mortality, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  # geom_boxplot(
  #   aes(x = cross, y = percent_mortality),
  #   alpha = 0.2,
  #   position = position_dodge(width = 0.5)
  # ) +
  # Add mean values as asterisks
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 8,  # asterisk shape
    size = 3,
    color = "red",
    position = position_dodge(width = 0.5),
    show.legend = FALSE
  ) +
  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("0:1", "1:1", "4:1", "8:1")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent F1 egg mortality", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig9d.png"),
  plot = p_f9d,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f9d
```
:::

# Figure 10

**Wrangling & Summary**

```{r}
#| label: fig10-wrangling

# Read and prepare data for Figure 10
df_f10a <- read_excel(here::here("analysis/data/Lincoln Tbas alone.xlsx"),
                    sheet = "Sheet1") |>
  janitor::clean_names() |>
  mutate(data = "Experiment")

df_f10b <- read_excel(here::here("analysis/data/Model Tbas alone_Tbas longev update.xlsx"),
                    sheet = "Sheet1") |>
  janitor::clean_names() |>
  select(ratio, percent_para) |>
  mutate(data = "Model")

# Combine experimental and model data
df_f10 <- rbind(df_f10a, df_f10b) |>
  mutate(ratio = as.factor(ratio),
         data = as.factor(data)
         )
rm(df_f10a, df_f10b)

# Check data structure
str(df_f10)
```

::: {.panel-tabset}
## Plot 1
```{r}
#| label: fig10-plota
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 10
p_f10a <- ggplot(df_f10,
       aes(x = ratio, y = percent_para, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  scale_y_log10(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("1:1", "1:2", "1:5")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent parasitism", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig10a.png"),
  plot = p_f10a,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f10a
```

## Models

No statistical model is fitted in this figure; panels compare experimental and model outputs descriptively.

## Plot 2
```{r}
#| label: fig10-plotb
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 10
p_f10b <- ggplot(df_f10,
       aes(x = ratio, y = percent_para, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
    geom_boxplot(
    aes(x = ratio, y = percent_para),
    alpha = 0.2,
    position = position_dodge(width = 0.5)
  ) +
  scale_y_log10(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("1:1", "1:2", "1:5")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent parasitism", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig10b.png"),
  plot = p_f10b,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f10b
```
## Plot 3
```{r}
#| label: fig10-plotc
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 10
p_f10c <- ggplot(df_f10,
       aes(x = ratio, y = percent_para, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  geom_boxplot(
    aes(x = ratio, y = percent_para),
    alpha = 0.2,
    position = position_dodge(width = 0.5)
  ) +
  # Add mean values as asterisks
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 8,  # asterisk shape
    size = 3,
    color = "red",
    position = position_dodge(width = 0.5),
    show.legend = FALSE
  ) +
  scale_y_log10(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("1:1", "1:2", "1:5")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent parasitism", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig10c.png"),
  plot = p_f10c,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f10c
```

## Plot 4
```{r}
#| label: fig10-plotd
#| fig-width: 5
#| fig-height: 4
#| dpi: 600

# Create plot for Figure 10
p_f10d <- ggplot(df_f10,
       aes(x = ratio, y = percent_para, fill = data, color = data)) +
  theme_classic() +
  theme(legend.position = "bottom") +
  geom_point(
    alpha = 0.22,
    position = position_jitterdodge(
      jitter.width = 0.3,
      jitter.height = 0,
      dodge.width = 0.5
    )
  ) +
  # geom_boxplot(
  #   aes(x = ratio, y = percent_para),
  #   alpha = 0.2,
  #   position = position_dodge(width = 0.5)
  # ) +
  # Add mean values as asterisks
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 8,  # asterisk shape
    size = 3,
    color = "red",
    position = position_dodge(width = 0.5),
    show.legend = FALSE
  ) +
  scale_y_log10(trans=scales::pseudo_log_trans(base = 10), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete(labels = c("1:1", "1:2", "1:5")) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_color_manual(values = c("grey50", "black")) +
  labs(x = "Overflooding ratio", y = "Percent parasitism", 
       color = "Data", fill = "Data") +
  facet_wrap(~data, nrow = 1)

ggsave(
  filename = here::here("outputs/plots", "fig10d.png"),
  plot = p_f10d,
  width = knitr::opts_current$get("fig.width"),
  height = knitr::opts_current$get("fig.height"),
  dpi = 600
)
p_f10d
```
:::

# References

R Core Team (2022). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. <https://www.R-project.org/>

Burnham, K. P., & Anderson, D. R. (2002). *Model selection and multimodel inference: A practical information-theoretic approach* (2nd ed.). Springer. (AICc / model selection.)

Fox, J., & Weisberg, S. (2019). *An R companion to applied regression* (3rd ed.). Sage.

Lenth, R. V. (2024). emmeans: Estimated marginal means, aka least-squares means. *Journal of Statistical Software*, 109(1), 1–48. <https://doi.org/10.18637/jss.v109.i01> (R package: <https://CRAN.R-project.org/package=emmeans>.)

Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., & Makowski, D. (2021). performance: An R package for assessment, comparison and testing of statistical models. *Journal of Open Source Software*, 6(60), 3139. <https://doi.org/10.21105/joss.03139>

Wickham, H. (2016). *ggplot2: Elegant graphics for data analysis*. Springer-Verlag. <https://ggplot2-book.org/>

Tukey, J. W. (1949). Comparing individual means in the analysis of variance. *Biometrics*, 5(2), 99–114. <https://doi.org/10.2307/3001913> (Tukey’s HSD / pairwise comparisons.)

::: {.callout-note collapse="true"}
## Session Information

```{r}
#| label: session-info
utils::sessionInfo()
```
:::